---
title: "stat_analysis_wk3"
author: "Daniel Mogere"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Check which packages are already installed, install others
pkgs <- c("dplyr", "ggplot2", "knitr","here","stats","corrplot")
miss_pkgs <- pkgs[!pkgs %in% installed.packages()[,1]] # vector of missing packages
if(length(miss_pkgs)>0){
  install.packages(miss_pkgs)}

## Load the packages
invisible(lapply(pkgs,library,character.only=TRUE))

rm(miss_pkgs, pkgs)
```

Load the clead data
```{r}
ad.cln<-read.csv(here("Clean_Data","adults_clean.csv"))
#make workclass factor
ad.cln$workclass<-as.factor(ad.cln$workclass)
```

Run the Logistic Regression test
```{r}
## Fit logistic regression model
logistic_model <- glm(income ~ workclass, data = ad.cln, family = binomial)
# Summarize the model
summary(logistic_model)
```
__Interpretation__

Herein I mention about percentage of likelihoo, I obtain the percentage by thsi formula

(exp(co-efficient)/(1+exp(co-efficient)))*100

__Work Class Fedral governenment__

The negative coefficient in the intercept, implies that, when the influence of the other working classes is held constant, an person working in the Federal government 38.6% less likely to earn greater than 50k. Statistically significant.
__Work Class Local governenment__

The negative coeffciient in the local government work class, indicates that working in the local government is associated with lower likelihood of earning >50K compared to working in fedearal government (38.1% less likely to earn >50K than working in Federal government).This relationship is statistically significant.

__Work Class Never Worked__

The negative coefficient indicates that, individual in the never worked work class are 99.99% less likely to earn greater than 50k than those in the federal government.However this is not statistically significant.

__Work Class Private__

The negative coefficient in this category indicate that, individual in the private work class, are 70.3% less likely to earn more than 50K than those working in Federal givernment. This is statistically significant

__Work Class Self-emp-inc__

The positive co-efficient in this category, indicate that individuals who are self employed and working in the corporate sector are 66.7% more likely to earn >50K than those in the federal government. This is statistically significant

__Work Class Self-emp-not-inc__

The negative coeffiecient, indicates that individuals who are self employed but not incorporated, are 61.3% less likely to earn more than 50K than those in the federal government.This is statistically significant

__Work Class State-gov__

The negatiev coeffciient indicates that, working in the state government is associated with 62.8% less probability of earning more than 50K as compared to working in the Federal government.

__Work Class Without pay__

The negative coefficient implies that working without pay is associated with 99.99% lesser probability of eraning more than 50K as compared to working with the federal governemnt. However, this is not statistically significant.


Run Logistic regression model for occupation versus income
```{r}
#Make occupation variable factor
ad.cln$occupation<-as.factor(ad.cln$occupation)
## Fit logistic regression model
logistic_model <- glm(income ~ occupation, data = ad.cln, family = binomial)
# Summarize the model
summary(logistic_model)
```
__Interpretation__

__Occupation Adm-Clerical__

Individuals in the Administrative clerical occupation are 13.4% less likely to earn more than 50K. Statistically significant

__Occupation Armed Forces__

Individuals in the Armed forces occupation are 44.6% less likely to earn more than 50K than those in the administrative clerical occupation. Not Statistically significant

__Occupation Exec Managerial__

Individuals in the Exec managerial occupation are 85.8% more likely to earn more than 50K than those in the administrative clerical occupation. Statistically significant

__Occupation Craft Repair__

Individuals in the Craft repair occupation are 65.4% more likely to earn more than 50K than those in the administrative clerical occupation. Statistically significant

__Occupation Farming Fishing__

Individuals in thefarminhg fishing occupation are 45.7% less likely to earn more than 50K than those in the administrative clerical occupation. Not Statistically significant

__Occupation  Handlers Cleaners__

Individuals who are handlers or cleaners are 30.1% less likely to earn more than 50K than those in the administrative clerical occupation. Statistically significant

__Occupation  Machine op Inspect__

Individuals who are machine operators or inspectors are 47.9% less likely to earn more than 50K than those in the administrative clerical occupation. Not Statistically significant

__Occupation  Other service__

Individuals who are in the other service occupation are 21.8% less likely to earn more than 50K than those in the administrative clerical occupation. Statistically significant


__Occupation  Private house service__

Individuals who are in the private house service occupation are 41.7% less likely to earn more than 50K than those in the administrative clerical occupation. Statistically significant

__Occupation  Prof speciality__

Individuals who are in the professional speciality occupation are 77% more likely to earn more than 50K than those in the administrative clerical occupation. Statistically significant.

__Occupation  Protective service__

Individuals who are in the professional speciality occupation are 75.6% more likely to earn more than 50K than those in the administrative clerical occupation. Statistically significant.

__Occupation  Sales__

Individuals who are in the sales occupation are 70% more likely to earn more than 50K than those in the administrative clerical occupation. Statistically significant.


__Occupation  Tech Support__

Individuals who are in the Tech support occupation are 73.8% more likely to earn more than 50K than those in the administrative clerical occupation. Statistically significant.

__Occupation  Transport moving__

Individuals who are in the Tech occupation are 61.7% more likely to earn more than 50K than those in the administrative clerical occupation. Statistically significant.

Check for correlation between number of hours per week, education level on income
```{r}
## Fit logistic regression model
logistic_model <- glm(income ~ education+hours.per.week, data = ad.cln, family = binomial)
# Summarize the model
summary(logistic_model)
```

__Interpretation__

The positive coefficient in the hours per week coefficient indicate that working an additional hour per week increases the likelihood of earning more than 50K by 51%.